Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-03-04 docs/manuscript/manuscript.tex
Updates from Overleaf

 \texttt{truc} & Tanker truck & 
\\\midrule
 \texttt{ctan} & Cart with tank & 
\\\midrule
 \texttt{bott} & Bottled water & Drinking water is bottled water/demi john.
\\\midrule
 \texttt{othw} & Other water source & 
\\\midrule
\texttt{surw} & Surface water
& 
\\\midrule
\texttt{tles} & Water 30 minutes or less away round trip
& 
\\\midrule 
\texttt{tmor} & Water more than 30 minutes away round trip & DHS Program Surveys
\\\midrule
 \texttt{watp} & Water on the premises
 & 
 \\\bottomrule
  \end{tabular}
  \caption{Summary of water accessibility variables (National Household usage Averages measured as percentage for Main Drinking Source)}
  \label{tab:summary-wa}
\end{table}

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Notes \\\midrule
 \texttt{bicy} & Bicycle
 & DHS Program Surveys
\\\midrule
 \texttt{acar} & Animal drawn cart
 & DHS Program Surveys
\\\midrule
 \texttt{mcyc} & Motorcycle
 & DHS Program Surveys
\\\midrule
 \texttt{pcar} & Private car
 & DHS Program Surveys
\\\midrule
 \texttt{cgdp} & GDP (current US \$) 
 & World Bank Data [NY.GDP.MKTP.CD]
\\\midrule
 \texttt{tpop} & Total Population
 & World Bank Data   [SP.POP.TOTL]
\\\midrule
 \texttt{upop} & Urban population 
 & World Bank Data  (\% of total population)  [SP.URB.TOTL.IN.ZS]
\\\midrule
 \texttt{popd} & Population density 
 & World Bank Data  (people per sq. km of land area)  [EN.POP.DNST]
\\\midrule
 \texttt{land} & Land area 
 & World Bank Data  (sq. km) [AG.LND.TOTL.K2]
\\\midrule
 \texttt{lita} & Literacy rate, adult total 
 & World Bank Data  (\% of people ages 15 and above) [SE.ADT.LITR.ZS]
\\\midrule
 \texttt{lity} & Literacy rate, youth 
 & World Bank Data  (ages 15-24), gender parity index (GPI) [SE.ADT.1524.LT.FM.ZS]
\\\midrule
 \texttt{mori} & Mortality rate, under-5 
 & World Bank Data  (per 1,000 live births) [SH.DYN.MORT]
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country (World Bank Data).

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Advanced Correlation Graph of Water Variables}
  \label{fig:cor-plot}
\end{figure}

>>>>

 \texttt{truc} & Tanker truck & 
\\\midrule
 \texttt{ctan} & Cart with tank & 
\\\midrule
 \texttt{bott} & Bottled water & Drinking water is bottled water/demi john.
\\\midrule
 \texttt{othw} & Other water source & 
\\\midrule
\texttt{surw} & Surface water
& 
\\\midrule
\texttt{tles} & Water 30 minutes or less away round trip
& 
\\\midrule 
\texttt{tmor} & Water more than 30 minutes away round trip & 
\\\midrule
 \texttt{watp} & Water on the premises
 & 
 \\\bottomrule
  \end{tabular}
  \caption{Summary of water accessibility variables (National Household usage Averages measured as percentage for Main Drinking Source)}
  \label{tab:summary-wa}
\end{table}

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Notes \\\midrule
 \texttt{bicy} & Bicycle
 & DHS Program Surveys
\\\midrule
 \texttt{acar} & Animal drawn cart
 & DHS Program Surveys
\\\midrule
 \texttt{mcyc} & Motorcycle
 & DHS Program Surveys
\\\midrule
 \texttt{pcar} & Private car
 & DHS Program Surveys
\\\midrule
 \texttt{cgdp} & GDP (current US \$) 
 & World Bank Data [NY.GDP.MKTP.CD]
\\\midrule
 \texttt{tpop} & Total Population
 & World Bank Data   [SP.POP.TOTL]
\\\midrule
 \texttt{upop} & Urban population 
 & World Bank Data  (\% of total population)  [SP.URB.TOTL.IN.ZS]
\\\midrule
 \texttt{popd} & Population density 
 & World Bank Data  (people per sq. km of land area)  [EN.POP.DNST]
\\\midrule
 \texttt{land} & Land area 
 & World Bank Data  (sq. km) [AG.LND.TOTL.K2]
\\\midrule
 \texttt{lita} & Literacy rate, adult total 
 & World Bank Data  (\% of people ages 15 and above) [SE.ADT.LITR.ZS]
\\\midrule
 \texttt{lity} & Literacy rate, youth 
 & World Bank Data  (ages 15-24), gender parity index (GPI) [SE.ADT.1524.LT.FM.ZS]
\\\midrule
 \texttt{mori} & Mortality rate, under-5 
 & World Bank Data  (per 1,000 live births) [SH.DYN.MORT]
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country (DHS Program).

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Advanced Correlation Graph of Water Variables}
  \label{fig:cor-plot}
\end{figure}
Next, we studied the explanatory variables that we collected and extracted from the World Bank Data.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{cor-wb}
  \caption{Advanced Correlation Graph of World Bank Explanatory Variables}
  \label{fig:cor-wb}
\end{figure}
